There are several internet resources which can provide help if you struggle with Traverso. Before posting a question, however, it is recommended to carefully classify your problem. The source packages released by the Traverso team are usually well tested and compile without too much tinkering. If you still fail to compile it on your system, the Traverso team will most probably refer you to the user forum of your distribution. You can make life easier for all of us by posting your question there in the first place. Thus we ask you to consider the following points before asking for help.

\section{Compilation fails}
Please make sure that you have installed all required packages listed in chapter \ref{sect_installation} of this document. If you still get the error, search the archive of the Traverso developer mailing list \cite{ml-archive} for the same problem. If you don't find a solution, send an e-mail with a description  and the compiler output attached to the developer mailing list (traverso-devel@nongnu.org) or file a support request on the Savannah project page \cite{support}. Chances are high that the problem is distribution-specific and that you will be asked to refer to the user forum of your distribution.

If you can track down the error to missing dependencies, please consider to seek advice in the distribution forum in the first place.

\section{Binary package fails to install}
Search the archive of the Traverso developer mailing list \cite{ml-archive} for the solution. If you don't find the answer, send an e-mail with an accurate description of the problem to the Traverso developer mailing list (traverso-devel@nongnu.org).

\section{Bugs}
Search the archive of the Traverso developer mailing list \cite{ml-archive} and the bug tracker on Savannah \cite{bugtracker} for discussions of the problem. If you don't find any references, report the bug with instructions for reproduction, relevant information on your hardware, and the version of the Qt library used, on the bug tracker \cite{bugtracker}.

%\section{Feature request}
%Please (!) ask yourself if it is realistic to implement the requested feature at the current stage of development. If yes, send an e-mail with a detailed description to the developer mailing list \cite{ml-archive}.

\section{Getting involved}
The Traverso team highly appreciates any kind of contribution. If you are C++ coder, artist, musician, translator, or bug hunter who wants to help making Traverso the best multitrack application ever, please offer your help on the developer mailing list (traverso-devel@nongnu.org).

